An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-29 paper/3.minbigul_m.tex
change Fig. -> Figure

When evaluating a composition of several programs in minBiGUL (and the same holds for full BiGUL), the same $get$s have to be evaluated repeatedly because no intermediate states are kept during the evaluation. This problem was illustrated in Fig.~\ref{fig:eval-comp-phead}. To avoid reevaluating $get$s, and as our first approach, we introduce memoization in the minBiGUL interpreter.
% can save 
To keep it simple, the intermediate states of a composition are saved in a key-value table where the key is a pair of program $bx$ and source $s$, and the value is the result of evaluating $\getbx{bx}{s}$ the first time. Then, instead of recomputing the value, the value in the table is used. The memoizing version, minBiGUL$_m$, needs only two modifications: $get_m$ and $put_m$ (Defs.~\ref{def:putm} and~\ref{def:getm}). Another function, $get_{mh}$, is used to retrieve the value of an already evaluated $get$ from the table or to compute an unevaluated $get$ by $get_m$ and store the key-value tuple in the table (Def.~\ref{def:getmh}).

>>>>

When evaluating a composition of several programs in minBiGUL (and the same holds for full BiGUL), the same $get$s have to be evaluated repeatedly because no intermediate states are kept during the evaluation. This problem was illustrated in Figure~\ref{fig:eval-comp-phead}. To avoid reevaluating $get$s, and as our first approach, we introduce memoization in the minBiGUL interpreter.
% can save 
To keep it simple, the intermediate states of a composition are saved in a key-value table where the key is a pair of program $bx$ and source $s$, and the value is the result of evaluating $\getbx{bx}{s}$ the first time. Then, instead of recomputing the value, the value in the table is used. The memoizing version, minBiGUL$_m$, needs only two modifications: $get_m$ and $put_m$ (Definitions~\ref{def:putm} and~\ref{def:getm}). Another function, $get_{mh}$, is used to retrieve the value of an already evaluated $get$ from the table or to compute an unevaluated $get$ by $get_m$ and store the key-value tuple in the table (Definition~\ref{def:getmh}).
